Bipartite Fidelity and Loschmidt Echo of the Bosonic Conformal Interface

### 2017-12-13 intro.tex
[prb] version accepted by prb.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
We compute the Loschmidt echo to extract information in the dynamics of the quench process of these models. The Loschmidt echo is the (square of the) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$. It decays with a power law $t^{- \alpha}$ for the lack of length scale in the $t \rightarrow \infty$ limit. The decay exponent $\alpha$ has been calculated for various geometries and combinations of normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. We extend the analysis to the aforementioned parametric interface of (possibly) different CFTs. We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transmission coefficients. Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. The finite size fidelity calculation further supports these results.

The rest of the paper is organized as follows. In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable bosonic conformal interface and its lattice realization. In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally, we conclude in Sec.~\ref{sec:conclusion}.

>>>>

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
We compute the Loschmidt echo to extract information in the dynamics of the quench process of these models. The Loschmidt echo is the (square of the) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$. It decays with a power law $t^{- \alpha}$ for the lack of length scale in the $t \rightarrow \infty$ limit. The decay exponent $\alpha$ has been calculated for various geometries and combinations of normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. We extend the analysis to the aforementioned parametric interface of (possibly) different CFTs. We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transmission coefficients. Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remaining $\frac{1}{4}$ otherwise. The finite size fidelity calculation further supports these results.

The rest of the paper is organized as follows. In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for the permeable bosonic conformal interface and its lattice realization. In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with the fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally, we conclude in Sec.~\ref{sec:conclusion}.

### 2017-12-13 num_result.tex
[prb] version accepted by prb.

We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results. Our numerical calculations are based on a boson Bogoliubov transformation and the explicit form of the groundstates. The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details. In all the figures, we present the coefficients of the logarithmic term $\frac{\mathcal{F}}{\ln L}$ and $\frac{\mathcal{F} }{\ln t}$ and call them fidelity and echo exponents respectively.

We first consider the process ${\rm DD} \rightarrow \lambda$
%in Eq.~\eqref{eq:DDDD}
%\begin{equation}
%\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
%\end{equation}
and show its Loschmidt echo of system size 30000 sites in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linearly decreasing behavior in the log-log scale indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD} as contrast). The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

We also calculated the companion process ${\rm NN} \rightarrow \lambda$ and obtain identical exponents as in Fig.~\ref{fig:DDDD}. We avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$. While the short time decay pattern is different from the DD case, the long-time behavior and exponents remain the same for both echo and fidelity. We therefore do not present the result here.

Next, we analyze the more interesting $\theta$ dependent process ${\rm DN} \rightarrow \lambda$
%in Eq.~\eqref{eq:DNDN}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the boundary condition after joining is determined by $S_1(\theta)$. We worked with a system containing $35000$ sites. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process (see the full notation in Eq.~\eqref{eq:Full_notation_rand()})
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta).
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of the power law decay, and the corresponding exponents follow the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. %We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

>>>>

We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results. Our numerical calculations are based on a boson Bogoliubov transformation and the explicit form of the groundstates. The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details. In all the figures, we present the coefficients of the logarithmic terms $\frac{\mathcal{F}}{\ln L}$ and $\frac{\mathcal{F} }{\ln t}$ and call them fidelity and echo exponents respectively.

We first consider the process ${\rm DD} \rightarrow \lambda$
%in Eq.~\eqref{eq:DDDD}
%\begin{equation}
%\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
%\end{equation}
and show its Loschmidt echo of system size 30000 sites in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linearly decreasing behavior in the log-log scale indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD} as contrast). The exponent (negative of the slope of the line in the log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

We also calculated the companion process ${\rm NN} \rightarrow \lambda$ and obtain identical exponents as in Fig.~\ref{fig:DDDD}. We avoid the technical subtlety of the zero mode by adding a small mass regulator $m=10^{-8}$. While the short time decay pattern is different from the DD case, the long-time behavior and exponents remain the same for both echo and fidelity. We therefore do not present the result here.

Next, we analyze the more interesting $\theta$ dependent process ${\rm DN} \rightarrow \lambda$
%in Eq.~\eqref{eq:DNDN}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the boundary condition after joining is determined by $S_1(\theta)$. We worked with a system containing $35000$ sites. A direct calculation with the mass regulator does not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process (see the full notation in Eq.~\eqref{eq:Full_notation_rand()})
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta).
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of the power law decay, and the corresponding exponents follow the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. %We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.
